The Astropy Project

### 2017-10-06 main.tex
Update on Overleaf.
astropy package is lower case

% Packages / projects / programming - for consistency!
\newcommand{\package}[1]{\texttt{#1}}
\newcommand{\github}{\package{GitHub}}
\newcommand{\python}{\package{Python}}
\newcommand{\astropy}{Astropy}
\newcommand{\astropypkg}{\package{Astropy}}

@@

@@

The \texttt{astropy.units} subpackage provides ...

@@

\begin{description}
    \item[Speed improvements] ...
    \item[Logarithmic units and magnitudes] ...
    \item[Interaction with \texttt{numpy} arrays] ...
\end{description}

@@

\begin{equation}
y = \frac{x - v_{vmin}}{v_{max} − v_{min}}
\end{equation}

@@

\section{Infrastructure for affiliated packages}
\label{sec:infrastructure}
\inlinecomment{BMS}{should we use links to the appropriate github repo?}
\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
%
\par In addition to astronomy related packages and libraries, the \astropy\
Project also contains and supports several infrastructure package that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsection{Package template}
% Brigitta may write this up if there is no other takers
\par \astropy\ provides a template package that any \python\ package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\texttt{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the \astropy\ ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for TravisCI and AppveyorCI.
%
\subsection{sphinx extensions}
% Tom R

@@

\section{The future of the Astropy project}
\label{sec:future}

>>>>

% Packages / projects / programming - for consistency!
\newcommand{\package}[1]{\texttt{#1}}
\newcommand{\github}{\package{GitHub}}
\newcommand{\python}{\package{Python}}
\newcommand{\astropy}{Astropy}
\newcommand{\astropypkg}{\package{astropy}}

@@

\subsection{Support of Astropy}

% This section should be a straight forward/factual description of the current
% funding and support provided to astropy with the purpose of explaining the 
% current structure to the community

@@

The \package{astropy.units} subpackage provides ...

@@

\begin{description}
    \item[Speed improvements] ...
    \item[Logarithmic units and magnitudes] ...
    \item[Interaction with \package{numpy} arrays] ...
\end{description}

@@

\begin{equation}
y = \frac{x - v_{vmin}}{v_{max} - v_{min}}
\end{equation}

@@

\section{Infrastructure for affiliated packages}
\label{sec:infrastructure}
\inlinecomment{BMS}{should we use links to the appropriate github repo?}
\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
%
\par In addition to astronomy related packages and libraries, the \astropy\
Project also contains and supports several infrastructure package that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsection{Package template}
% Brigitta may write this up if there is no other takers
\par \astropy\ provides a template package that any \python\ package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\package{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the \astropy\ ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for TravisCI and AppveyorCI.
%
\subsection{sphinx extensions}
% Tom R

@@

\section{The future of the Astropy project}
\label{sec:future}
\subsection{Roadmap for \python\ 3 only support}
